---
title: "Hashtag Based R Code"
author: "Preethi"
date: "5/22/2019"
output: html_document
---

Packages necessary to run the code

```{r include = FALSE}
install.packages("qdap")
install.packages("qdapRegex")
install.packages("qdapDictionaries")
install.packages("RColorBrewer")
install.packages("qdapTools")
install.packages("twitteR")
install.packages("ROAuth")
install.packages("plyr")
install.packages("dplyr")
install.packages("stringr")
install.packages("ggplot2")
install.packages("rtweet")


```


Including the libraries 
```{r include=FALSE}
library(twitteR) 
library(ROAuth) 
library(plyr) 
library(dplyr) 
library(stringr)
library(ggplot2)
library(rtweet)
library(qdap)

```
Create an app in twitter developer community 
Retrieve the api key , api secret key , accesstoken & secret access token from twitter API  

```{r}
appname <- 'Hashtag Based Sentiment Analysis'
apikey <- ''
apiSecretKey <- ''
accessToken <- ''
accessTokenSecret <- ''
requestUrl <- 'https://api.twitter.com/oauth/request_token'
accessUrl <- 'https://api.twitter.com/oauth/access_token'
OAuthUrl <- 'https://api.twitter.com/oauth/authorize'

```

```{r}
download.file(url='http://curl.haxx.se/ca/cacert.pem', destfile='cacert.pem')
Credentials <- OAuthFactory$new(consumerKey = apikey , consumerSecret= apiSecretKey ,requestURL = requestUrl,accessURL = accessUrl, authURL = OAuthUrl )
```

```{r}
Credentials$handshake(cainfo = system.file('CurlSSL', 'cacert.pem', package = 'RCurl'))
```
```{r}
save(Credentials, file='Hashtag Based Sentiment Analysis twitter authentication.Rdata')
load('Hashtag Based Sentiment Analysis twitter authentication.Rdata')

```

```{r}
setup_twitter_oauth(apikey,apiSecretKey,access_token = accessToken,access_secret = accessTokenSecret)
```


SearchInTwitter Function Passes the Hashtag to twitter api and retrieves the 
data (around 1500 tweets that uses the hashtag) , cleans the tweets and process the data , compares each tweet against the positive and negative data file and assigns scores to individual tweet , create a plot about reactions according to data 
```{r}
SearchInTwitter<- function(HashtagTerm)
{

Datalist <- searchTwitter(HashtagTerm,n=1500,lang ="en" )
#Datalist = strip_retweets(Datalist)

 DataFrame <- twListToDF(Datalist)

#Order by Column names 
 DataFrame <- DataFrame [, order(names(DataFrame))]
View(DataFrame)

#Filling with created date 
 DataFrame$created <- strftime(DataFrame$created, '%Y-%m-%d')


 if (file.exists(paste(HashtagTerm, '_tweets.csv'))==FALSE) 
 write.csv(DataFrame, file=paste(HashtagTerm, '_tweets.csv'), row.names=F)

 Data <- read.csv(file=paste(HashtagTerm, '_tweets.csv'))
 Data <- rbind(Data, DataFrame)
 Data <- subset(Data, !duplicated(Data$text))
 write.csv(Data, file=paste(HashtagTerm, '_tweets.csv'), row.names=F)

#creates a file called Patriots_tweets.csv with all the tweets and if the #file exists , it merges the data set with the existing data set and #remove the duplicate data in the new file . 
#Scores the tweets based on no of positive and negative words . 

#folder with positive dictionary


positive <- scan('~/Desktop/positive-words.txt', what='character', comment.char=';') 
#folder with negative dictionary

negative <- scan('~/Desktop/negative-words.txt', what='character', comment.char=';') 
positive.words <- c(positive)
negative.words <- c(negative)
Dataset <- Data
Dataset$text <- as.factor(Dataset$text)

evaluvate.Tweet <- function(tweets , positive.words, negative.words, .progress='none')
{
require(plyr)
require(stringr)

#For each element of a list, apply function then combine results into an array.

Tweetscores <- laply ( tweets , function(tweet, positive.words, negative.words){

#Data Processing steps in phase 2 
tweet <- str_replace_all(tweet,"#[a-z,A-Z]*","")

tweet <- str_replace_all(tweet,"@[a-z,A-Z]*","")   
tweet = gsub("[^\x01-\x7F]", "", tweet) 
tweet = gsub(" ?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)", "", tweet)
tweet = gsub('[[:punct:]]', "", tweet)
tweet = gsub("\\n", "", tweet)
tweet = tolower (tweet)
tweet_list <- str_split(tweet, "\\s")
View(tweet)
words <- unlist(tweet_list)
words <- rm_stopwords(words, tm::stopwords("english"))
View(words)

positive.matches <- match(words, positive.words)
negative.matches <- match(words, negative.words)
positive.matches <- !is.na(positive.matches)
negative.matches <- !is.na(negative.matches)
score <- sum(positive.matches) - sum(negative.matches)
View(score)
return(score)

}, positive.words, negative.words, .progress=.progress)
 Tweetscores.df <- data.frame(score= Tweetscores, text=tweets)
 return(Tweetscores.df)

}

#Ends evaluvate.Tweet

#calling the function to evaluvate the tweet 
scores <- evaluvate.Tweet(Dataset$text, positive.words, negative.words, .progress='text')
View(Scores)

#saving evaluation results(score) into the file
 write.csv(scores, file=paste(HashtagTerm, '_tweets.csv'), row.names=TRUE)  #total evaluation: positive / negative / neutral
 
stat <- scores
stat$created <- as.Date (Data$created)
 
#Assigns Value as positive ,negative or neutral based on the score 
stat <- mutate(stat, dt=ifelse(stat$score > 0, 'positive', ifelse(stat$score < 0, 'negative', 'neutral')))

#grouping by date and score 
 by.dt <- group_by(stat, dt, created)
 
by.dt <- summarise(by.dt, number=n())
# writing to the grouped data to csv file 
 write.csv(by.dt, file=paste(HashtagTerm, '_grouped.csv'), row.names=TRUE)

ggplot(by.dt, aes(created, number)) + geom_line(aes(group=dt, color=dt), size=2) +
 geom_point(aes(group=dt, color=dt), size=4) +
 theme(text = element_text(size=18), axis.text.x = element_text(angle=90, vjust=1)) +
 #stat_summary(fun.y = 'sum', fun.ymin='sum', fun.ymax='sum', colour = 'yellow', size=2, geom = 'line') +
 ggtitle(HashtagTerm)
ggsave(file=paste(HashtagTerm, '_plot.jpeg'))

}

SearchInTwitter ("#Patriots")

```

This downloads and updates the Plot each day